Tail Indices and Scale Parameters in Financial Time Series

### 2017-03-30 papers/FX/draft.tex
Revised the part about estimation of shifted pareto distributions.

\section{Empirical Results}
\label{sec:empirical_results}
As has been mentioned, we are interested in the heavy-tail properties
of equity returns. Let $X_t$ be an equity return series. If the
distribution of $X_t$ is heavy-tailed, we can write
\begin{eqnarray*}
  \lim_{x \to \infty} {x^{\beta}\P(X_t > x) \over L_+(x)} &=& 1 \\
  \lim_{x \to \infty} {x^{\alpha}\P(X_t < -x) \over L_-(x)} &=& 1
\end{eqnarray*}
where $L_+(x)$ and $L_-(x)$ are slowly varying functions satisfying
\[
\lim_{x \to \infty} {L_*(a x) \over L_*(x)} = 1
\]
for all $a > 0$. Here ``*'' can be either ``+'' or ``-''. In the
simplest case, $L_+(x)$ and $L_(x)$ are constants and the distribution
has power-law tails. Let $J_*(1/x) = L_*(x)$. A Taylor expansion at
$x=\infty$ gives
\[
J_*(1/x) = J_*(0) + {J'_*(0) \over x} + O(x^{-2})
\]
Thus
\[
x^{-\alpha} L_-(x) = J_-(0) x^{-\alpha} + J'_-(0) x^{-\alpha - 1} + O(x^{-\alpha-2})
\]
when $x \to \infty$. Clearly the tail indices $\alpha$ and $\beta$ as
well as the scale parameters $J_-(0)$ and $J_+(0)$ play crutial roles
in determining the tail distribution and hence in asset allocation and
risk management. These parameters of the equities in a market are
characteristics of the market and provide a useful description of the
market. One can also use them to help build a model of the equities in
the market. With these motives in mind, we present a survey of the
tail indices and scale parameters of 3 sectors, namely ``Energy'',
``Consumer Staples'' and ``Information Technology'', of the S\&P 500
index.

\subsection{Hill estimates of lower tail indices}
\label{sec:Hill}
There have been several estimators for the tail index proposed in the
literature, e.g. Hill (1975) \cite{hill1975simple}, Pikands (1975)
\cite{pickands1975statistical}, Dekkers and Einmahl and De Haan (1989)
\cite{dekkers1989moment}. See also Embrechts and Kl\"uppelberg and
Mikosch (1997)\cite{Embrechts1997}. The most popular of these is
arguably Hill (1975) \cite{hill1975simple}:
\[
\hat \alpha = \left[
  {1 \over k} \sum_{i=1}^k \ln {x_{(i)} \over x_{(k+1)}}
  \right]^{-1}
\]
where $x_{(i)}$ is the $i$-th upper order statistic of a sample
$x_1, x_2, ..., x_n$. It has been shown that the Hill estimator is
applicable to 
\begin{itemize}
\item iid random variables (Mason (1982) \cite{mason1982laws})
\item a weakly dependent sequence (Rootz{\'e}n, Leadbetter,
  and de Haan \cite{rootzen1992tail})
\item a linear process (Resnick and St{\u{a}}ric{\u{a}} (1995)
  \cite{resnick1995consistency}).
\end{itemize}
In these cases it is shown that, if $k \to \infty$ and $k/n \to 0$
as $n \to \infty$, the Hill estimator is weakly consistent, i.e.
\[
\sqrt k (\hat \alpha - \alpha) \overset{d}{\to} N(0, \alpha^2)
\]

@@

\subsection{Hill estimates of lower-tail scale parameters}

@@

\subsection{Pareto-distributed equity return}
In this section, we look into the situation when $X$ has a shifted
Pareto distribution. Assume
\begin{equation}
  \label{eq:X_distr}
  F(x) = \left\{
  \begin{array}{ll}
    p \left(
    {K \over K - x}
    \right)^\alpha & x \leq 0 \\
    1 - (1 - p) \left(
    {K' \over K' + x}
    \right)^\beta & x > 0
  \end{array}
  \right.
\end{equation}
Assume $\alpha, \beta > 1$, $0 < p < 1$ and $K > 0$.
We have
\begin{eqnarray}
  && \mathcal U F (\alpha, \beta, K, K', \phi) \nonumber \\
  &=&
  \alpha K^\alpha  p
  \int_{-\infty}^0
  u\left[ (1 - \phi) e^r + \phi e^x \right]
  {1 + b \over (K - x)^{\alpha + 1}} dx
  \nonumber \\
  &&
  \beta K'^\beta (1 - p)
  \int_{0}^\infty
  u\left[ (1 - \phi) e^r + \phi e^x \right]
  {1 + b \1{x < q} \over (K' + x)^{\beta + 1}} dx 
  - b u(\delta v) F(q)
  % &&
  % - b u(\delta v) \left[
  %   1 - (1 - p) {
  %     K'^\beta
  %     \over
  %     (K' + q)^\beta
  %   }
  % \right]
  \label{eq:xxie1.0}
\end{eqnarray}
\begin{theorem}
  \label{thrm:I}
  Suppose functional $G(\cdot)$ is given as \eqref{eq:G_functional},
  function $u(\cdot)$ is increasing and differentiable, then
  \[
  \pd{G(F)}{\alpha} > 0,
  \quad
  \pd{G(F)}{K} < 0
  \]
\end{theorem}
Since $u(v)$ given in \eqref{eq:xxie1.0} as a
functional of the distribution function of $X$ is increasing with the
lower tail index $\alpha$ and decreasing with $K$, there is a curve of
equal preference on the plane of $(\alpha, K)$. Moving along this
curve in the direction of increasing $\alpha$, one expects the values
of $K$ to increase too, i.e. the estimated values of $\alpha$ and $K$
should appear positively correlated. This is indeed the case in some
real stock return data, e.g. the ``Energy'' and ``Information Technology''
sectors of S\&P 500 companies. This is illustrated in figures
\ref{fig:Energy_alpha_K} and \ref{fig:Information_Technology_alpha_K}.
The confidence bands of the Hill estimates of $\alpha$ of these
sectors are shown in figures \ref{fig:Energy_lower},
\ref{fig:Consumer_Staples_lower} and
\ref{fig:Information_Technology_lower}.

\begin{proof}
  Let
  \begin{equation}
    \label{eq:xxie2}
    \hat \phi := \argmax_{0 < \phi \leq 1} \mathcal U(F, \phi)
  \end{equation}
  We have
  \[
  G(F) = \mathcal U(F, \hat\phi)
  \]
  It follows
  \begin{eqnarray}
    \pd{G(F)}{\alpha}
    &=&
    \pd{\mathcal U(F, \phi)}{\alpha}(\alpha, K, \hat\phi)
    + \pd{\mathcal U(F, \phi)}{\phi}(\alpha, K, \hat\phi)
    \pd{\hat\phi}{\alpha}(\alpha, K)
    \label{eq:xxie3}
  \end{eqnarray}
  The definition \eqref{eq:xxie2} implies $\forall \alpha > 1$
  \begin{equation}
    \label{eq:xxie4}
    \pd{\mathcal U(F, \phi)}{\phi}(\alpha, K, \hat \phi) = 0
  \end{equation}
  So the second term of \eqref{eq:xxie3} vanishes. It remains to show
  \begin{eqnarray*}
    \pd{\mathcal U(F, \phi)}{\alpha}(\alpha, K, \hat \phi)
    &>& 0
  \end{eqnarray*}
  From \eqref{eq:xxie1.0}, it follows
  \begin{eqnarray*}
    \pd{\mathcal U(F, \phi)}{\alpha}(\alpha, K, \hat\phi)
    = \opd{\alpha}\E[u((1 - \hat\phi) e^r + \hat\phi e^X) \1{X < 0}]
  \end{eqnarray*}
  The function $u((1 - \hat\phi) e^r + \hat\phi e^X)$ is obviously increasing
  with $X$. It follows
  \begin{eqnarray*}
    && \pd{f(x; \alpha, K)}{\alpha} \\
    &=& \opd{\alpha} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} \\
    &=&
    - {K^\alpha \over (K - x)^{\alpha + 1}}
    \left[
      \alpha
      \ln\left(
        1 - {x \over K}
      \right) - 1
    \right]
  \end{eqnarray*}
  It is easily checked that when $x < K(1 - e^{1/\alpha}) < 0$,
  \[
  \opd{\alpha} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} < 0
  \]
  and when $K(1 - e^{1/\alpha}) < x < 0$,
  \[
  \opd{\alpha} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} > 0
  \]
  This is the second case of lemma \ref{lemma:I}. So we have
  \begin{eqnarray*}
    \pd{\mathcal U(F, \phi)}{\alpha}(\alpha, K, \hat\phi) &>& 0
  \end{eqnarray*}
  As for $\pd{G(F)}{K}$, by the same argument as for
  $\pd{G(F)}{\alpha}$, it suffices to show
  \[
  \pd{\mathcal U(F, \phi)}{K}(\alpha, K, \hat\phi) < 0
  \]
  We have
  \[
  \pd{\mathcal U(F, \phi)}{K}(\alpha, K, \hat\phi)
  = \opd{K} \E \left[
    u((1 - \hat\phi) e^r + \hat\phi e^X) \1{X < 0}
  \right] 
  \]
  and
  \begin{eqnarray*}
    && \pd{f(x; \alpha, K)}{K} \\
    &=& \opd{K} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} \\
    &=&
    -\alpha K^{\alpha - 1} {
      \alpha x + K
      \over
      (K - x)^{\alpha + 2}
    }
  \end{eqnarray*}
  Clearly, when $x < -\alpha/K$
  \[
  \opd{K} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} > 0
  \]
  and when $-\alpha/K < x < 0$
  \[
  \opd{K} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} < 0
  \]
  So by the 1st case of remark \ref{remark:I} we conclude
  \[
  \pd{\mathcal U(F, \phi)}{K}(\alpha, K, \hat\phi) < 0  
  \]
\end{proof}
By numerically integration and optimization with respect to $\phi$,
the value of $\hat\phi$ can be obtained for given $u(\cdot)$ and given
values of $K, K', \alpha, \beta$. Figures \ref{fig:phi_hat_pareto5e-1}
and \ref{fig:phi_hat_pareto4} show the values of $\hat\phi$ for
$u(C) = -\frac{C^{-\xi}}{\xi}$ with $\xi = 1/2, 4$ respectively.
$\beta=\alpha$ and $K'=K$ in both figures.
\begin{figure}
  \begin{subfigure}[b]{0.5\linewidth}
    \includegraphics[width=\textwidth]{phi_hat_pareto5e-1.pdf}
    \caption{$\hat\phi$ when $\xi = 1/2$}
    \label{fig:phi_hat_pareto5e-1}
  \end{subfigure}
  \begin{subfigure}[b]{0.5\linewidth}
    \includegraphics[width=\textwidth]{phi_hat_pareto4.pdf}
    \caption{$\hat\phi$ when $\xi = 4$}
    \label{fig:phi_hat_pareto4}
  \end{subfigure}
  \caption{$\hat\phi$, the optimal equity allocation when the utility
    function is $u(C) = -{C^{-\xi} \over \xi}$ for $\xi = 1/2, 4$.
  }
\end{figure}

@@

Figure \ref{fig:Energy_alpha_K},
\ref{fig:Consumer_Staples_alpha_K},
and \ref{fig:Information_Technology_alpha_K}
show the estimates of $K$ alongside the Hill estimates of $\alpha$ of
the ``energy'', ``consumer staples'' and ``information
technology'' sectors of the S\&P 500 index, respectively.
\begin{figure}[htb!]
  \centering
  \begin{subfigure}[b]{0.45\linewidth}
    \includegraphics[width=\textwidth]
                    {Energy_alpha_K.pdf}
                    \caption{``Energy''}
                    \label{fig:Energy_alpha_K}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\linewidth}
    \includegraphics[width=\textwidth]
                    {Energy_alpha_K_ci.pdf}
                    \caption{``Energy''}
                    \label{fig:Energy_alpha_K_ci}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\linewidth}
    \includegraphics[width=\textwidth]
                    {Consumer_Staples_alpha_K.pdf}
                    \caption{``Consumer Staples''}
                    \label{fig:Consumer_Staples_alpha_K}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\linewidth}
    \includegraphics[width=\textwidth]
                    {Consumer_Staples_alpha_K_ci.pdf}
                    \caption{``Consumer Staples''}
                    \label{fig:Consumer_Staples_alpha_K_ci}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\linewidth}
    \includegraphics[width=\textwidth]
                    {Information_Technology_alpha_K.pdf}
                    \caption{``Information Technology''}
                    \label{fig:Information_Technology_alpha_K}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\linewidth}
    \includegraphics[width=\textwidth]
                    {Information_Technology_alpha_K_ci.pdf}
                    \caption{``Information Technology''}
                    \label{fig:Information_Technology_alpha_K_ci}
  \end{subfigure}
  \caption{\small Maximum likelihood estimates of $K$, the scale
    parameter, of stocks in sectors of the S\&P 500 index. The points
    are the
    estimated values; the bars are the upper bound of the 98\%
    confidence interval. The lower bound is 0.
  }
\end{figure}

@@

First notice that when $b = 0$, $\mathcal U(F, \phi)$ reduces to
$\E u(C(X, \phi))$. Only the first integral of \eqref{eq:t1} remains.
Its integrand becomes $\ln[C(x, \phi) C(-x, \phi)]$.
Now observe $\ln(C(x, \phi)C(-x, \phi))$ is an increasing function of
$x$:
\begin{eqnarray*}
  \pd{C(x, \phi) C(-x, \phi)}{x}
  &=&
  \phi e^r (1 - \phi) (e^x - e^{-x}) > 0
\end{eqnarray*}
Thus when $b = 0$, by 1st case of remark \ref{remark:I} and lemma
\ref{lemma:II},
$\pd{\mathcal U(F, \phi))}{\nu} < 0$ for all $\phi$. Hence all
investors guided by this utility function would be seeking the
smallest $\nu$, i.e. the heaviest tail in the market. Here note that
Student's t is a symmetric distribution; heavier tails imply greater
down-side risk as well as greater up-side potential.

@@

>>>>

\section{Empirical Results}
\label{sec:empirical_results}
As has been mentioned, we are interested in the heavy-tail properties
of equity returns. Let $X_t$ be an equity return series. If the
distribution of $X_t$ is heavy-tailed, we can write
\begin{eqnarray*}
  \lim_{x \to \infty} {x^{\beta}\P(X_t > x) \over L_+(x)} &=& 1 \\
  \lim_{x \to \infty} {x^{\alpha}\P(X_t < -x) \over L_-(x)} &=& 1
\end{eqnarray*}
where the constants $\alpha$ and $\beta$ are left and right tail
indices, respectively, and $L_+(x)$ and $L_-(x)$ are slowly varying
functions satisfying
\[
\lim_{x \to \infty} {L_*(a x) \over L_*(x)} = 1
\]
for all $a > 0$. Here ``*'' can be either ``+'' or ``-''. In the
simplest case, $L_+(x)$ and $L_(x)$ are constants and the distribution
has power-law tails. Let $J_*(1/x) = L_*(x)$. A Taylor expansion at
$x=\infty$ gives
\begin{equation}
  \label{eq:scale_parameter}
  J_*(1/x) = J_*(0) + {J'_*(0) \over x} + O(x^{-2})
\end{equation}
Thus
\begin{equation}
  \label{eq:lower_tail_expansion}
  x^{-\alpha} L_-(x) =
  J_-(0) x^{-\alpha} + J'_-(0) x^{-\alpha - 1} + O(x^{-\alpha-2})
\end{equation}
when $x \to \infty$. Clearly the tail indices $\alpha$ and $\beta$ as
well as the scale parameters $J_-(0)$ and $J_+(0)$ play crutial roles
in determining the tail distribution and hence in asset allocation and
risk management. These parameters of the equities in a market are
characteristics of the market and provide a useful description of the
market. One can also use them to help build a model of the equities in
the market. With these motives in mind, we present a survey of the
tail indices and scale parameters of 3 sectors, namely ``Energy'',
``Consumer Staples'' and ``Information Technology'', of the S\&P 500
index.

\subsection{Hill estimates of lower tail indices}
\label{sec:Hill}
There have been several estimators for the tail index proposed in the
literature, e.g. Hill (1975) \cite{hill1975simple}, Pikands (1975)
\cite{pickands1975statistical}, Dekkers and Einmahl and De Haan (1989)
\cite{dekkers1989moment}. See also Embrechts and Kl\"uppelberg and
Mikosch (1997)\cite{Embrechts1997}. The most popular of these is
arguably Hill (1975) \cite{hill1975simple}:
\begin{equation}
  \label{eq:Hill_index}
  \hat \alpha = \left[
    {1 \over k} \sum_{i=1}^k \ln {x_{(i)} \over x_{(k+1)}}
    \right]^{-1}
\end{equation}
where $x_{(i)}$ is the $i$-th upper order statistic of a sample
$x_1, x_2, ..., x_n$. It has been shown that the Hill estimator is
applicable to 
\begin{itemize}
\item iid random variables (Mason (1982) \cite{mason1982laws})
\item a weakly dependent sequence (Rootz{\'e}n, Leadbetter,
  and de Haan \cite{rootzen1992tail})
\item a linear process (Resnick and St{\u{a}}ric{\u{a}} (1995)
  \cite{resnick1995consistency}).
\end{itemize}
In these cases it is shown that, if $k \to \infty$ and $k/n \to 0$
as $n \to \infty$, the Hill estimator is weakly consistent, i.e.
\[
\sqrt k (\hat \alpha - \alpha) \overset{d}{\to} N(0, \alpha^2)
\]

@@

\subsection{Hill estimates of lower-tail scale parameters}
\label{sec:HillScaleEstimates}

For convenience, we denote the scale parameter by $A$. It is the
constant $J_*(0)$ in the Taylor expansion \eqref{eq:scale_parameter}.
Hill \cite{hill1975simple} put forward an estimator of $A$ using his
tail index  estimator:
\[
\hat A = {k \over n} X_{(k+1)}^{\hat \alpha}
\]
where $X_{(k+1)}$ is the $(k+1)$-th upper order statistic of the
sequence $X_t$ as defined in section\ref{sec:Hill}.

@@

\subsection{Pareto-distributed equity return}
In this section, we look into the situation when $X$ has a shifted
Pareto distribution. Assume
\begin{equation}
  \label{eq:X_distr}
  F(x) = \left\{
  \begin{array}{ll}
    p \left(
    {K \over K - x}
    \right)^\alpha & x \leq 0 \\
    1 - (1 - p) \left(
    {K' \over K' + x}
    \right)^\beta & x > 0
  \end{array}
  \right.
\end{equation}
Assume $\alpha, \beta > 1$, $0 < p < 1$ and $K > 0$.
We have
\begin{eqnarray}
  && \mathcal U F (\alpha, \beta, K, K', \phi) \nonumber \\
  &=&
  \alpha K^\alpha  p
  \int_{-\infty}^0
  u\left[ (1 - \phi) e^r + \phi e^x \right]
  {1 + b \over (K - x)^{\alpha + 1}} dx
  \nonumber \\
  &&
  \beta K'^\beta (1 - p)
  \int_{0}^\infty
  u\left[ (1 - \phi) e^r + \phi e^x \right]
  {1 + b \1{x < q} \over (K' + x)^{\beta + 1}} dx 
  - b u(\delta v) F(q)
  % &&
  % - b u(\delta v) \left[
  %   1 - (1 - p) {
  %     K'^\beta
  %     \over
  %     (K' + q)^\beta
  %   }
  % \right]
  \label{eq:xxie1.0}
\end{eqnarray}
\begin{theorem}
  \label{thrm:I}
  Suppose functional $G(\cdot)$ is given as \eqref{eq:G_functional},
  function $u(\cdot)$ is increasing and differentiable, then
  \[
  \pd{G(F)}{\alpha} > 0,
  \quad
  \pd{G(F)}{K} < 0
  \]
\end{theorem}
The proof of theorem \ref{thrm:I} is given in secton
\ref{sec:thrmI_proof}.
Since $u(v)$ given in \eqref{eq:xxie1.0} as a
functional of the distribution function of $X$ is increasing with the
lower tail index $\alpha$ and decreasing with $K$, there is a curve of
equal preference on the plane of $(\alpha, K)$. Moving along this
curve in the direction of increasing $\alpha$, one expects the values
of $K$ to increase too, i.e. the estimated values of $\alpha$ and $K$
should appear positively correlated. This is indeed the case in some
real stock return data, e.g. the ``Energy'', ``Consumer Staples'' and
``Information Technology'' sectors of S\&P 500 companies. This is
illustrated in figures 
\ref{fig:Energy_alpha_K_ci}, \ref{fig:Consumer_Staples_alpha_K_ci}
and \ref{fig:Information_Technology_alpha_K_ci}.
The confidence bands of the Hill estimates of $\alpha$ of these
sectors are shown in figures \ref{fig:Energy_lower},
\ref{fig:Consumer_Staples_lower} and
\ref{fig:Information_Technology_lower}.

By numerically integration and optimization with respect to $\phi$,
the value of $\hat\phi$ can be obtained for given $u(\cdot)$ and given
values of $K, K', \alpha, \beta$. Figures \ref{fig:phi_hat_pareto5e-1}
and \ref{fig:phi_hat_pareto4} show the values of $\hat\phi$ for
$u(C) = -\frac{C^{-\xi}}{\xi}$ with $\xi = 1/2, 4$ respectively.
$\beta=\alpha$ and $K'=K$ in both figures.
\begin{figure}
  \begin{subfigure}[b]{0.5\linewidth}
    \includegraphics[width=\textwidth]{phi_hat_pareto5e-1.pdf}
    \caption{$\hat\phi$ when $\xi = 1/2$}
    \label{fig:phi_hat_pareto5e-1}
  \end{subfigure}
  \begin{subfigure}[b]{0.5\linewidth}
    \includegraphics[width=\textwidth]{phi_hat_pareto4.pdf}
    \caption{$\hat\phi$ when $\xi = 4$}
    \label{fig:phi_hat_pareto4}
  \end{subfigure}
  \caption{$\hat\phi$, the optimal equity allocation when the utility
    function is $u(C) = -{C^{-\xi} \over \xi}$ for $\xi = 1/2, 4$.
  }
\end{figure}

@@

To obtain an estimate of $p$, we use the law of large number:
\begin{eqnarray*}
  p &=& \P(X < 0) = \lim_{n \to \infty}
  {1 \over n} \sum_{t=1}^n \1{X_t < 0}
\end{eqnarray*}
By the central limit theorem,
\begin{eqnarray*}
  \sqrt n \left[
    {1 \over n}\sum_{t=1}^n \1{X_t < 0} - p
  \right] \to N(0, p - p^2))
\end{eqnarray*}

Figure \ref{fig:Energy_alpha_K_ci},
\ref{fig:Consumer_Staples_alpha_K_ci},
and \ref{fig:Information_Technology_alpha_K_ci}
show the estimates of $K$ alongside the Hill estimates of $\alpha$ of
the ``energy'', ``consumer staples'' and ``information technology''
sectors of the S\&P 500 index, respectively.
Figure \ref{fig:Energy_p}, \ref{fig:Consumer_Staples_p} and
\ref{fig:Information_Technology_p} show the estimates of $p$ of the
same sectors.

From these figures, one can see that stocks of the ``Energy'' and the
``Information Technology'' sectors generally have larger values of
$p$, meaning their stock prices fall more often than do those in the
``consumer Staples'' sector; Also, the values of $K$ in the ``Energy''
and ``Information Technology'' sectors are larger than those in the
``Consumer Staples'' sector. A larger value of $K$ means, for a given
value of $p$, i.e. a given probability of losses, large losses are
more probable. Thus one can conclude that these two sectors are
considerablly riskier than the ``Consumer Staples'' sector. This is of
course a confirmation of one's economic instinct.

One can also see from figure \ref{fig:Energy_alpha_K_ci}
and \ref{fig:Information_Technology_alpha_K_ci} that, while the
``Energy'' and the ``Information Technology'' sectors are similar in
riskiness, the correlation between $\alpha$ and $K$ is stronger in
``Energy''. As discussed in the last section, moving along a curve of
equal preference in the direction of increasing $\alpha$, $K$ also
increases. So the strong positive correlation seen in the ``Energy''
sector suggests these stocks might have very similar investor
preferences. This in turn may be attributed to stronger business
relations between the energy enterprises. While two IT companies
may provide a variety of products and services and not depend on each
other, two energy companies are more likely to depend on each other
via relations of supplier and customer or otherwise to compete with each
other if they are on the same link of the chain of energy production
and distribution.

\begin{figure}[htb!]
  \centering
  \begin{subfigure}[b]{0.45\linewidth}
    \includegraphics[width=\textwidth]
                    {Energy_p.pdf}
                    \caption{``Energy''}
                    \label{fig:Energy_p}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\linewidth}
    \includegraphics[width=\textwidth]
                    {Energy_alpha_K_ci.pdf}
                    \caption{``Energy''}
                    \label{fig:Energy_alpha_K_ci}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\linewidth}
    \includegraphics[width=\textwidth]
                    {Consumer_Staples_p.pdf}
                    \caption{``Consumer Staples''}
                    \label{fig:Consumer_Staples_p}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\linewidth}
    \includegraphics[width=\textwidth]
                    {Consumer_Staples_alpha_K_ci.pdf}
                    \caption{``Consumer Staples''}
                    \label{fig:Consumer_Staples_alpha_K_ci}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\linewidth}
    \includegraphics[width=\textwidth]
                    {Information_Technology_p.pdf}
                    \caption{``Information Technology''}
                    \label{fig:Information_Technology_p}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\linewidth}
    \includegraphics[width=\textwidth]
                    {Information_Technology_alpha_K_ci.pdf}
                    \caption{``Information Technology''}
                    \label{fig:Information_Technology_alpha_K_ci}
  \end{subfigure}
  \caption{\small Estimates of $p$ and $K$ of stocks in sectors of the
    S\&P 500 index. The points are the estimated values; the bars are
    the $2\sigma$ confidence intervals.
  }
\end{figure}
To compare the maximum likelihood estimates with the results obtained
from Hill's scale estimates, one can re-write the lower-tail
distribution function: For all $x < 0$,
\begin{eqnarray*}
  \P(X < x)
  &=&
  p {K^\alpha \over (K - x)^\alpha} \\
  &=&
  p {K^\alpha |x|^{-\alpha} \over (1 - K/x)^\alpha} \\
  &=&
  p K^\alpha |x|^{-\alpha} \left(
  1 + {\alpha K \over x} + O(|x|^{-2})
  \right)
\end{eqnarray*}
Comparing this expression with \eqref{eq:lower_tail_expansion}, one
can immediately identity $p K^\alpha$ as the scale parameter.

@@

First notice that when $b = 0$, $\mathcal U(F, \phi)$ reduces to
$\E u(C(X, \phi))$. Only the first integral of \eqref{eq:t1} remains.
Its integrand becomes $\ln[C(x, \phi) C(-x, \phi)]$.
Now observe $\ln(C(x, \phi)C(-x, \phi))$ is an increasing function of
$x$:
\begin{eqnarray*}
  \pd{C(x, \phi) C(-x, \phi)}{x}
  &=&
  \phi e^r (1 - \phi) (e^x - e^{-x}) > 0
\end{eqnarray*}
Thus when $b = 0$, by 1st case of remark \ref{remark:I} and lemma
\ref{lemma:II},
$\pd{\mathcal U(F, \phi))}{\nu} < 0$ for all $\phi$. Hence all
investors guided by this utility function would be seeking the
smallest $\nu$, i.e. the heaviest tail in the market. Here note that
Student's t is a symmetric distribution; a heavier tail implies not
only greater down-side risk but also greater up-side potential.

@@

\section{Proof of Theorem \ref{thrm:I}}
\label{sec:thrmI_proof}
\begin{proof}
  Let
  \begin{equation}
    \label{eq:xxie2}
    \hat \phi := \argmax_{0 < \phi \leq 1} \mathcal U(F, \phi)
  \end{equation}
  We have
  \[
  G(F) = \mathcal U(F, \hat\phi)
  \]
  It follows
  \begin{eqnarray}
    \pd{G(F)}{\alpha}
    &=&
    \pd{\mathcal U(F, \phi)}{\alpha}(\alpha, K, \hat\phi)
    + \pd{\mathcal U(F, \phi)}{\phi}(\alpha, K, \hat\phi)
    \pd{\hat\phi}{\alpha}(\alpha, K)
    \label{eq:xxie3}
  \end{eqnarray}
  The definition \eqref{eq:xxie2} implies $\forall \alpha > 1$
  \begin{equation}
    \label{eq:xxie4}
    \pd{\mathcal U(F, \phi)}{\phi}(\alpha, K, \hat \phi) = 0
  \end{equation}
  So the second term of \eqref{eq:xxie3} vanishes. It remains to show
  \begin{eqnarray*}
    \pd{\mathcal U(F, \phi)}{\alpha}(\alpha, K, \hat \phi)
    &>& 0
  \end{eqnarray*}
  From \eqref{eq:xxie1.0}, it follows
  \begin{eqnarray*}
    \pd{\mathcal U(F, \phi)}{\alpha}(\alpha, K, \hat\phi)
    = \opd{\alpha}\E[u((1 - \hat\phi) e^r + \hat\phi e^X) \1{X < 0}]
  \end{eqnarray*}
  The function $u((1 - \hat\phi) e^r + \hat\phi e^X)$ is obviously
  increasing with $X$. It follows
  \begin{eqnarray*}
    && \pd{f(x; \alpha, K)}{\alpha} \\
    &=& \opd{\alpha} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} \\
    &=&
    - {K^\alpha \over (K - x)^{\alpha + 1}}
    \left[
      \alpha
      \ln\left(
        1 - {x \over K}
      \right) - 1
    \right]
  \end{eqnarray*}
  It is easily checked that when $x < K(1 - e^{1/\alpha}) < 0$,
  \[
  \opd{\alpha} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} < 0
  \]
  and when $K(1 - e^{1/\alpha}) < x < 0$,
  \[
  \opd{\alpha} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} > 0
  \]
  This is the second case of lemma \ref{lemma:I}. So we have
  \begin{eqnarray*}
    \pd{\mathcal U(F, \phi)}{\alpha}(\alpha, K, \hat\phi) &>& 0
  \end{eqnarray*}
  As for $\pd{G(F)}{K}$, by the same argument as for
  $\pd{G(F)}{\alpha}$, it suffices to show
  \[
  \pd{\mathcal U(F, \phi)}{K}(\alpha, K, \hat\phi) < 0
  \]
  We have
  \[
  \pd{\mathcal U(F, \phi)}{K}(\alpha, K, \hat\phi)
  = \opd{K} \E \left[
    u((1 - \hat\phi) e^r + \hat\phi e^X) \1{X < 0}
  \right] 
  \]
  and
  \begin{eqnarray*}
    && \pd{f(x; \alpha, K)}{K} \\
    &=& \opd{K} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} \\
    &=&
    -\alpha K^{\alpha - 1} {
      \alpha x + K
      \over
      (K - x)^{\alpha + 2}
    }
  \end{eqnarray*}
  Clearly, when $x < -\alpha/K$
  \[
  \opd{K} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} > 0
  \]
  and when $-\alpha/K < x < 0$
  \[
  \opd{K} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} < 0
  \]
  So by the 1st case of remark \ref{remark:I} we conclude
  \[
  \pd{\mathcal U(F, \phi)}{K}(\alpha, K, \hat\phi) < 0  
  \]
\end{proof}
